---
title: "Assignment 10"
author: "Group 5"
date: "2023-11-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

(a) Load in the data using read.csv(). You will need to select header=F.
```{r}
df = read.csv(file="Ch10Ex11.csv" , header=F)
```

B)
```{r}
hc.complete <- hclust(as.dist(1 - cor(df)), method = "complete")
hc.single <- hclust(as.dist(1 - cor(df)), method = "single")
hc.average <- hclust(as.dist(1 - cor(df)), method = "average")

plot(hc.complete,main="Complete Linkage", xlab = "", sub="", cex=0.9)
plot(hc.average,main="Average Linkage", xlab = "", sub="", cex=0.9)
plot(hc.single,main="Single Linkage", xlab = "", sub="", cex=0.9)

table(predicted=cutree(hclust(as.dist(1 - cor(df)), method = "complete"), k=2), truth =c(rep(1,20), rep(2,20)))
table(predicted=cutree(hclust(as.dist(1 - cor(df)), method = "single"), k=2), truth =c(rep(1,20), rep(2,20)))
table(predicted=cutree(hclust(as.dist(1 - cor(df)), method = "average"), k=2), truth =c(rep(1,20), rep(2,20)))
```

C)
```{r}
Predicted = cutree(hclust(as.dist(1 - cor(df)), method = "complete"), k= 2)
DF = t(df)
DF_1 = DF[Predicted ==1,]
DF_1 = cbind(DF_1, Predict_cluster = 1)
DF_2 = DF[Predicted ==2,]
DF_2 = cbind(DF_2, Predict_cluster = 2)
DF = rbind(DF_1, DF_2)
library(randomForest)
result = randomForest(Predict_cluster~., data = DF, mtry = 5, ntree = 1000, importance = TRUE)
varImpPlot(result)
```

```{r}

# Make a distance matrix
D = as.dist(1-cor(df))
plot(hclust(D, method="complete"),main ="Complete Linkage", cex=0.9)

```

b) Apply hierarchical clustering to the samples using correlation-based distance, and plot the dendrogram. Do the genes separate the samples into the two groups? Do your results depend on the type of linkage used?
```{r}
#Step 1
hc.complete = hclust(dist(df), method = "complete")

hc.average = hclust(dist(df), method = "average")

hc.single = hclust(dist(df), method = "single")

par(mfrow=c(1,3))

plot(hc.complete,main="Complete Linkage", xlab = "", sub="", cex=0.9)

plot(hc.average,main="Average Linkage", xlab = "", sub="", cex=0.9)

plot(hc.single,main="Single Linkage", xlab = "", sub="", cex=0.9)

par(mfrow=c(1,1))
```


(c) Your collaborator wants to know which genes differ the most across the two groups. Suggest a way to answer this question, and apply it here.
```{r}
library(randomForest)
result = randomForest(predict_cluster~, data=df, mtry=5, ntree=1000, importance= TRUE)
varImpPlot(result)
```
