---
title: "Group Assignment 6"
author: "Young Kim"
date: "2023-10-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Exercise 6.8: Problem 9 (parts a, b, c, & d)

Problem 9. In this exercise, we will predict the number of applications received using the other variables in the College data set.

(a) Split the data set into a training set and a test set.
```{r}
library(ISLR)
data(College)
train = sample(1:nrow(College), nrow(College)/2)
test = (-train)
College.train = College[train,]
College.test = College[test,]
```

(b) Fit a linear model using least squares on the training set, and report the test error obtained.

```{r}
lm.fit = lm(Apps~.-Apps, data=College.train)

lm.pred = predict(lm.fit, College.test)

mean((lm.pred - College.test$Apps)^2)
```

(c) Fit a ridge regression model on the training set, with λ chosen by cross-validation. Report the test error obtained.
```{r}
train.mat <- model.matrix(Apps~.-Apps, data = College.train)
test.mat <- model.matrix(Apps~.-Apps, data = College.test)
grid <- 10 ^ seq(10, -2, length = 100)
fit.ridge <- glmnet(train.mat, College.train$Apps, alpha = 0, lambda = grid, thresh = 1e-12)
cv.ridge <- cv.glmnet(train.mat, College.train$Apps, alpha = 0, lambda = grid, thresh = 1e-12)
bestlam.ridge <- cv.ridge$lambda.min
bestlam.ridge

```
```{r}
pred.ridge <- predict(fit.ridge, s = bestlam.ridge, newx = test.mat)
mean((pred.ridge - College.test$Apps)^2)
```

(d) Fit a lasso model on the training set, with λ chosen by cross-validation. Report the test error obtained, along with the number of non-zero coefficient estimates.
```{r}
fit.lasso <- glmnet(train.mat, College.train$Apps, alpha = 1, lambda = grid, thresh = 1e-12)
cv.lasso <- cv.glmnet(train.mat, College.train$Apps, alpha = 1, lambda = grid, thresh = 1e-12)
bestlam.lasso <- cv.lasso$lambda.min
bestlam.lasso
```
```{r}
pred.lasso <- predict(fit.lasso, s = bestlam.lasso, newx = test.mat)
mean((pred.lasso - College.test$Apps)^2)
```
```{r}
#The test MSE is also higher for ridge regression than for least squares.
predict(fit.lasso, s = bestlam.lasso, type = "coefficients")

```

